\textbf{Evaluating RISC-V Enclaves:}\\ Security Without the Slowdown?

### 2025-09-05 draft_presentation.tex
added new diagrams

\end{tikzpicture}
\caption{Unbatched vs Batched enclave-to-host calls}
\end{figure}

@@

\only<5>{
\begin{alertblock}{Key Principle}
    \textbf{Optimize the trade-off:} Balance performance, isolation, and PMP resource usage for maximum efficiency.
\end{alertblock}
}
\end{frame}

>>>>

\end{tikzpicture}
%\caption{Unbatched vs Batched enclave-to-host calls}
\end{figure}

@@

\only<5>{
\begin{alertblock}{Key Principle}
\textbf{Balance system trade-offs:} Align enclave design with workload needs, considering performance, security, and hardware constraints.
\end{alertblock}
\begin{center}
\begin{tikzpicture}[scale=0.9, every node/.style={font=\scriptsize}, thick]
    % Define colors
    \colorlet{perfcol}{blue!60}
    \colorlet{isocol}{red!60}
    \colorlet{pmpcol}{green!60}

    % Draw overlapping circles
    \begin{scope}[blend group=multiply]
        \fill[perfcol, opacity=0.4] (90:1.4) circle (1.4);
        \fill[isocol, opacity=0.4] (210:1.4) circle (1.4);
        \fill[pmpcol, opacity=0.4] (330:1.4) circle (1.4);
    \end{scope}

    % Circle labels
    \node[font=\bfseries] at (90:2.3) {Performance};
    \node[font=\bfseries] at (210:2.3) {Security};
    \node[font=\bfseries] at (330:2.3) {HW Constraints};

    % Center label
    \node[fill=white, draw=black!30, rounded corners=2pt, font=\scriptsize, inner sep=2pt] 
        at (0,0) {\textbf{Balanced Trade-off}};

    % Optional: title above
    % \node[font=\bfseries\small] at (0,3.2) {Deployment Trade-off Space};
\end{tikzpicture}
\end{center}
}
\end{frame}
